Hypertension and microbiome

### 2019-09-04 articletwo.Rmd
Parallel
Minor

```{r deseq2}
pseq.genus.core.deseq <- pseq.genus %>% core(detection = 0.0001, prevalence = 0.01)

@@

ds2 <- estimateSizeFactors(dds.data, type="poscounts")
dds <- DESeq(ds2)

res <- results(dds)
df <- as.data.frame(res)
df$taxon <- rownames(df)

df$model.str <- modelstr
df$covariate <- variables[nv]

df %>% kable
```

>>>>

```{r deseq2}
pseq.genus.core.deseq <-  prune_taxa(taxa(pseq.genus.core), pseq.genus)

@@

ds2 <- estimateSizeFactors(dds.data, type="poscounts")

dds <- DESeq(ds2, fitType='mean', parallel = TRUE, BPPARAM=MulticoreParam(16))

results(dds) %>%
    as.data.frame %>%
    kable
```
